---
title: "253 Data Processing Long Term Record"
date: "Last Knitted `r format(Sys.Date(), '%d %b %Y')`"
author: "Last edit by: ACF  | Created by: ACF"
output: 
  html_document:
    df_print: paged
    number_sections: no
    toc: yes
    toc_float: true
    toc_depth: 3
    code_folding: show
editor_options: 
  chunk_output_type: inline
---

```{r install, eval = FALSE}
#devtools::install_github("KopfLab/isoreader", forse = TRUE)
#devtools::install_github("cubessil/isoprocessCUBES", forse = TRUE) #general CUBESsil lab stuff
#devtools::install_github("cubessil/CUBESSILclumpedmath", force = TRUE) #only for processing clumped data
```

```{r setup, message = FALSE, warning = FALSE}
library(rlang)
library(plotly)
library(isoreader)
library(tidyverse)
library(isoprocessCUBES)
library(CUBESSILclumpedmath)
```

# Data processing changes for each 253 session

#### - Populate session information based on template below.
#### - Copy/paste from your data reduction code for each session that renames, alters metadata, or culls analysis numbers. 
#### - Accumulate sessions from most recent to least.





___TEMPLATE START___

### TEMPLATE: "Analysis Range" - "User" - "Session Name"

User <- "__" -- make a list if more than one user for this time period. ex: c(ACF, BDK, JOV)

session <-"__" -- name you gave your session

session_date_start <- ####### -- use format "20200925"

session_date_end <- ####### -- use format "20200925"

session_analysis_start <- #####

session_analysis_end <- #####

```{r Data correction info - template}

#change the code chunk name to include "Analysis # Range" - "User" - "Session Name"
#use R chunk to compile all data processing changes you made throughout your 253 session 
#comment out whole chunk by highlighting all text in chunk and use crl+shift+c . if you leave it uncommented, this Rmarkdown won't knit 

```

___TEMPLATE END___






### 48525 to 52232 - ACF - AF11

User <- "ACF, BJDK"

session <-"AF11" -- name you gave your session

session_date_start <- 20210302 

session_date_end <- 20210429

session_analysis_start <- 48525

session_analysis_end <- 52232

```{r 48525 to 52232 - ACF - AF11}
# # put these 3 lines under the "clumped math" chunk in p1 code, need to edit the prep and ID 2 before trying to batch, otherwise batching plot won't work
# rawdata[  rawdata$Analysis > 49135 & rawdata$Analysis < 49140.99, "Identifier 1"] <- "ACF$all$zero" #20210312, c/p error for naming of zero, adding user
# rawdata[  rawdata$Analysis > 49135 & rawdata$Analysis < 49140.99, "Identifier 2"] <- "0" #20210312, c/p error for naming of zero, adding user
# rawdata[  rawdata$Analysis > 49135 & rawdata$Analysis < 49140.99, "Preparation"] <- "z" #20210312, c/p error for naming of zero, adding Preparation 
# 
# #TEMPLATE for AF11 session
# #flatlist.Cyc <- flatlist.Cyc %>% change.donotuse.and.runinfo(#####, #####.99, TRUE, "COMMMENT") #DATE #FURTHER NOTES
# 
# # Notes from this run
# #   Heated gases hadn't been fired since 09/2020, I ran one dR and eSSB before I remembered to refire them, for 4 hours at 1000C in furnace. refired dR_1000 on 03/09/2020 and refired eSSB_1000 on 03/10/2021
# #   --- interesting experiment to show how heated gases reequilibrate to room temperature over time.
# #   
# 
# #marking "Donotuse" or adding comment
# flatlist.Cyc <- flatlist.Cyc %>% 
# #HG - old fire
#   change.donotuse.and.runinfo(48645, 48654.99, TRUE, "Hadn't been fired since 09/20 (~6 months before). D47 much lower than expected") %>% #20210305, dR_1000, D47 much lower than expected. HG not fired since September 2020
#   change.donotuse.and.runinfo(48655, 48664.99, FALSE, "Hadn't been fired since 09/20 (~6 months before). D47 much lower than expected") %>% #20210305, eSSB_1000, HG not fired since September 2020
#   change.donotuse.and.runinfo(48700, 48709.99, FALSE, "Potentially contaminated std vial? Doesn't have high 48, but from same suspect vial") %>% #ETH1, Doesn't have high 48, but from same suspect vial
#   
# ## ETH1 high 48 - first  
#   change.donotuse.and.runinfo(48760, 48769.99, TRUE, "High d48background, d48sd, D48 excess. Contaminated std vial?") %>% #20210307, ETH1, high d48background, d48sd, D48 excess. Contaminated std vial?
#   change.donotuse.and.runinfo(48770, 48779.99, TRUE, "Elevated 48 background, following ETH1 with high d48 bkgrd and D48 excess") %>% #20200307, ETH3, d48 background high but decreasing
# #HG - old fire
#   change.donotuse.and.runinfo(48780, 48789.99, TRUE, "Elevated 48 background, following ETH1 with high d48 bkgrd and D48 excess. Hadn't been fired since 09/20 (~6 months before).") %>% #20200307, dR_1000, d48 background high but decreasing. HG not fired since September 2020
#   change.donotuse.and.runinfo(48790, 48799.99, TRUE, "Elevated 48 background, following ETH1 with high d48 bkgrd and D48 excess. Contaminated std vial?") %>% #20200307, ETH1 d48 background high but decreasing. Contaminated std vial?
#   change.donotuse.and.runinfo(48800, 48809.99, TRUE, "Elevated 48 background, following ETH1 with high d48 bkgrd and D48 excess. Stir stick maybe thrown?") %>% #20200307, ETH2, d48 background high but decreasing
#   change.donotuse.and.runinfo(48810, 48819.99, FALSE, "1st sample that 48bkgrd looks back to normal after high d48 from ETH1. Stir stick maybe thrown?") %>% #20210308, ETH2, stir stick maybe thrown?
#   change.donotuse.and.runinfo(48820, 48829.99, FALSE, "48bkgrd looks back to normal after high d48 from ETH1. Stir stick thrown") %>% #20210308, ETH3, stir stick maybe thrown
# 
# ## ETH1 high 48 - second  
#   change.donotuse.and.runinfo(48830, 48839.99, TRUE, "High d48background, d48sd, D48 excess. stir stick thrown. Contaminated std vial?") %>% #20210308, ETH1, high d48background, d48sd, D48 excess. Stir stick maybe thrown. Contaminated std vial?
# #HG - old fire
#   change.donotuse.and.runinfo(48840, 48849.99, TRUE, "Elevated 48 background, following ETH1 with high d48 bkgrd and D48 excess. Hadn't been fired since 09/20 (~6 months before).") %>% #202103, eSSB_1000
#   change.donotuse.and.runinfo(48850, 48859.99, TRUE, "Elevated 48 background, following ETH1 with high d48 bkgrd and D48 excess.") %>% #20210308, dR_25, double shot
#   change.donotuse.and.runinfo(48860, 48869.99, TRUE, "Elevated 48 background, following ETH1 with high d48 bkgrd and D48 excess.") %>% #20210308, CU YULE
#   change.donotuse.and.runinfo(48870, 48879.99, TRUE, "no gas, carousel error?") %>% #20210308, ETH1, no gas...? potential carousel error, makes sense bc next sample doesn't match ETH2 values 
#   change.donotuse.and.runinfo(48880, 48889.99, TRUE, "carousel error? no gas for sample before, and this one does not match ETH2 bulk values or D47") %>% #20210308, labeled as ETH2, but doesnt match population.... mystery?! also HUGE yield... combination of the powder before? but no stir stick issue...
#   change.donotuse.and.runinfo(48890, 48899.99, FALSE, "1st sample that 48bkgrd looks back to normal after high d48 from ETH1.") %>% #20210308, AF-NCF-TS2-17-21.5C, 48 background back to low levels
#   
#   change.donotuse.and.runinfo(48980, 48989.99, FALSE, "Potentially contaminated std vial? Doesn't have high 48, but from same suspect vial") %>% #ETH1
#   change.donotuse.and.runinfo(49010, 49019.99, TRUE, "high std residual. Contaminated std vial?") %>% #20210310, ETH1
#   change.donotuse.and.runinfo(49030, 49039.99, TRUE, "high std residual") %>%  #20210310, ETH3
#   change.donotuse.and.runinfo(49080, 49089.99, FALSE, "Potentially contaminated std vial? Doesn't have high 48, but from same suspect vial") %>% #ETH1
# #HG - new fire
#   change.donotuse.and.runinfo(49131, 49134.99, TRUE, "accidently pumped 1/2 of dR away. fired 03/09/2021") %>% #20210312, dR_1000, sequence user error, pumped away, newly fired
# #HG - new fire
#   change.donotuse.and.runinfo(49141, 49150.99, FALSE, "fired 03/10/2021") %>%  #20210312, eSSB_1000, fired by ACF on 03/10/2021, compare to previous HG that were fired in 09/20
#   change.donotuse.and.runinfo(49151, 49160.99, FALSE, "Stir stick maybe thrown?") %>%  #20210312, ETH2, 8.22mg
#   change.donotuse.and.runinfo(49161, 49170.99, FALSE, "Stir stick maybe thrown? watch for yield issue") %>% #20210312, AF-NCF-TS-323-A.dark ... run another replicate in case of yield issue
#   change.donotuse.and.runinfo(49171, 49180.99, FALSE, "Stir stick maybe thrown? watch for yield issue") %>% #20210313, ETH3, 8.59mg
# ## NEW STANDARD VIAL OF ETH1 opened on 03/12/2021 -- Analysis 49201
#   change.donotuse.and.runinfo(49201, 49210.99, FALSE, "first replicate of new ETH1 standard vial opened by ACF on 03/12/2021") %>%#20210313, ETH1
# #did something get contaminated or messed up? 
#   change.donotuse.and.runinfo(49426, 49435.99, TRUE, "high std deviation") %>%#20210316 ETH3
#   change.donotuse.and.runinfo(49446, 49455.99, TRUE, "rep different than the rest in D47 and bulk isos") %>% #20210316, ETH2 cull 
#   change.donotuse.and.runinfo(49456, 49465.99, TRUE, "rep different than the rest in D47 and bulk isos") %>% #20210316, ETH1 cull 
#   change.donotuse.and.runinfo(49506, 49515.99, TRUE, "rep different than the rest in D47 and bulk isos") %>% #20210317, ETH4
#   change.donotuse.and.runinfo(49516, 49525.99, TRUE, "rep different than the rest in D47 and bulk isos") %>% #20210317, ETH2
#   change.donotuse.and.runinfo(49526, 49535.99, TRUE, "rep different than the rest in D47 and bulk isos") %>%  #20210317, TS-323-A.dark, cull later?
#   change.donotuse.and.runinfo(49536, 49545.99, TRUE, "rep different than the rest in D47 and d18O") %>% #20210317, TS2-17-21.5D
#   change.donotuse.and.runinfo(49557, 49566.99, TRUE, "high std residuals") %>% #20210318 ETH3
#   change.donotuse.and.runinfo(51113, 51122.99, TRUE, "rep diff in D47 and D48") %>% #20210412, dR_25
#   change.donotuse.and.runinfo(51462, 51471.99, TRUE, "rep diff in D47 and D48") %>% #20210417, ETH4
#   change.donotuse.and.runinfo(51492, 51501.99, TRUE, "rep diff in D47 and D48") %>%  #20210417, ETH2
#   change.donotuse.and.runinfo(51472, 51481.99, FALSE, "between two high D48 std, watch") %>%  #20210417 TS-323-A.light
#   change.donotuse.and.runinfo(51482, 51491.99, FALSE, "between two high D48 std, watch") %>%  #20210417 TS3-16-10
#   change.donotuse.and.runinfo(51552, 51552.99, TRUE, "bad acq") %>%  #20210418 TS3-16-13
#   change.donotuse.and.runinfo(51512, 51512.99, TRUE, "bad acq") %>%  #20210418  TS3-16-20.gen2
#   change.donotuse.and.runinfo(51599.8, 51599.9, TRUE, "outlier cycle") %>%  #ACF$Knc$AF-NCF-TS2-17-21.5A.dark
#   change.donotuse.and.runinfo(51602.4, 51602.5, TRUE, "outlier cycle") %>%  #ACF$Knc$AF-NCF-TS2-17-21.5A.dark
#   change.donotuse.and.runinfo(51630.1, 51630.2, TRUE, "outlier cycle") %>%  #ACF$Knc$AF-NCF-TS2-17-21.5E.light 
#   change.donotuse.and.runinfo(49731.1, 49731.2, TRUE, "outlier cycle") %>%  #ACF$Knc$AF-NCF-TS3-16-10
#   change.donotuse.and.runinfo(51559.4, 51559.5, TRUE, "outlier cycle") %>%  #ACF$Knc$AF-NCF-TS3-16-05
#   change.donotuse.and.runinfo(51567.1, 51567.2, TRUE, "outlier Acq") %>%  #AF$Knc$AF-NCF-TS3-16-05  
#   change.donotuse.and.runinfo(51738, 51747.99, TRUE, "high std residual") %>%  #20210423, ETH2
#   change.donotuse.and.runinfo(51869, 51878.99, TRUE, "high std residual") %>%  #20210423, ETH2
#   change.donotuse.and.runinfo(52029, 52038.99, FALSE, "new ETH3 vial, opened by ACF 04/23/2021") %>% 
#   change.donotuse.and.runinfo(52129, 52138.99, FALSE, "new ETH3 vial, opened by ACF 04/23/2021") %>% 
#   change.donotuse.and.runinfo(52199, 52208.99, FALSE, "last of older ETH3 vial") #ETH3, new vial opened by ACF 04/23/2021
# 
# #renaming
# flatlist.Cyc[  flatlist.Cyc$Analysis > 48880 & flatlist.Cyc$Analysis < 48889.99, "Identifier 1"] <- "ACF$all$gasmix" #20210311, labeled as ETH2, but is a mixture of gases bc of carousel error 
# flatlist.Cyc[  flatlist.Cyc$Analysis > 49060 & flatlist.Cyc$Analysis < 49069.99, "Identifier 1"] <- "ACF$all$ETH2" #20210311, mislabeled as ETH3 in runlist, should be ETH2
# flatlist.Cyc[  flatlist.Cyc$Analysis > 49135 & flatlist.Cyc$Analysis < 49140.99, "Identifier 1"] <- "ACF$all$zero" #20210312, c/p error for naming of zero, adding user
# flatlist.Cyc[  flatlist.Cyc$Analysis > 49135 & flatlist.Cyc$Analysis < 49140.99, "Preparation"] <- "z" #20210312, c/p error for naming of zero, adding Preparation
# flatlist.Cyc[  flatlist.Cyc$Analysis > 49873 & flatlist.Cyc$Analysis < 49882.99, "Identifier 1"] <- "ACF$all$ETH1" #carousel error caused mislabelling, ETH1 mislabled as ETH4
# flatlist.Cyc[  flatlist.Cyc$Analysis > 49883 & flatlist.Cyc$Analysis < 49892.99, "Identifier 1"] <- "ACF$all$ETH4" #carousel error caused mislabelling, ETH4 mislabled as ETH3
# flatlist.Cyc[  flatlist.Cyc$Analysis > 49893 & flatlist.Cyc$Analysis < 49902.99, "Identifier 1"] <- "ACF$all$ETH3" #carousel error caused mislabelling, ETH3 mislabelled as ETH2
# flatlist.Cyc[  flatlist.Cyc$Analysis > 51548 & flatlist.Cyc$Analysis < 51557.99, "Identifier 1"] <- "ACF$Knc$AF-NCF-TS3-16-13" # didn't use the 13.gen2.light bottled used original TS3-16-13
# flatlist.Cyc[  flatlist.Cyc$Analysis > 51598 & flatlist.Cyc$Analysis < 51607.99, "Identifier 1"] <- "ACF$Knc$AF-NCF-TS2-17-21.5A.dark" #used "." instead of "-"
# flatlist.Cyc[  flatlist.Cyc$Analysis > 52089 & flatlist.Cyc$Analysis < 52098.99, "Identifier 1"] <- "ACF$all$dR_1000" 
# 
# #Missed a dR_25 and so some data needs to be moved up one.
# flatlist.Cyc <- getmetadatafromAnalysis(flatlist.Cyc, 50141, 50150.99, 50131)
# flatlist.Cyc <- getmetadatafromAnalysis(flatlist.Cyc, 50131, 50140.99, 50121)
# flatlist.Cyc <- getmetadatafromAnalysis(flatlist.Cyc, 50121, 50130.99, 50111)
# flatlist.Cyc[  flatlist.Cyc$Analysis > 50111 & flatlist.Cyc$Analysis < 50120.99, "Identifier 1"] <- "BJDK$all$dR_25"
# flatlist.Cyc[  flatlist.Cyc$Analysis > 50111 & flatlist.Cyc$Analysis < 50120.99, "Identifier 2"] <- "0" 
# 
# # The carousel went haywire and then got stuck. Analaysis 50304 to 50343 either has no gas or did not drop.
# flatlist.Cyc <- flatlist.Cyc %>% 
#           change.donotuse.and.runinfo(50304, 50343.99, TRUE, "carousel stoped working correctly") %>%  
#           change.donotuse.and.runinfo(50304, 50343.99, TRUE, "carousel stoped working correctly")
# flatlist.Cyc <- getmetadatafromAnalysis(flatlist.Cyc, 50515, 50515.99, 50514)# last basic aq for ETH3 got the lable for the next ETH4
# flatlist.Cyc[  flatlist.Cyc$Analysis > 50515 & flatlist.Cyc$Analysis < 50515.99, "batch"] <- 171 #fix the batch number so Sample.ID works correctly
# flatlist.Cyc[  flatlist.Cyc$Analysis > 50586 & flatlist.Cyc$Analysis < 50595.99, "Identifier 1"] <- "ACF$all$ETH3" #the seq didn't match the paper runlist
# flatlist.Cyc[  flatlist.Cyc$Analysis > 50586 & flatlist.Cyc$Analysis < 50595.99, "Identifier 2"] <- "8.89"
# #50515
# 
```


### 42224 to 44648 - ACF - AF10

User <- "ACF" 

session <-"AF10" 

session_date_start <- 20200802

session_date_end <- 20200909

session_analysis_start <- 42224

session_analysis_end <- 44648

```{r 42224 to 44648 - ACF - AF10}
# #Code examples: 
# #flatlist.Cyc[  flatlist.Cyc$Analysis > 28131 & flatlist.Cyc$Analysis < 28139.8, "Identifier 1"] <- "all$dR_1000"  
# #flatlist.Cyc[ flatlist.Cyc$`Identifier 1` == "KB_CI_576; EBOC" , "Identifier 1"] <- "eBOC_1000"
# #flatlist.Cyc <- getmetadatafromAnalysis(flatlist.Cyc, 28207, 28215.7, 28198) #Can use this function to shift the metadata from one set of analysis numbers to another set; useful for occasions like carousel glitches or starting the sequence on the wrong line that result in the wrong sample information for a given sample
# 
# #TEMPLATE for AF10 session
# #flatlist.Cyc <- flatlist.Cyc %>% change.donotuse.and.runinfo(#####, #####.99, TRUE, "COMMMENT") #DATE #FURTHER NOTES
# 
# #marking "Donotuse" or adding comment
# flatlist.Cyc <- flatlist.Cyc %>% 
#   change.donotuse.and.runinfo(42266, 42275.99, TRUE, "eSSB_25, way colder than rest of pop in D47") %>% #20200803 #eSSB_25
#   change.donotuse.and.runinfo(42306, 42315.99, TRUE, "unchecked pressure balance for some acquisitions") %>% #20200803 #ETH3, accidently left pressure balance button unchecked for a few acqusitions, and poor yield, didn't fully digest in acid
#   change.donotuse.and.runinfo(42326, 42326.99, TRUE, "1 acq, trial gas") %>% #20200804 #SH$SHgasAug
#   change.donotuse.and.runinfo(42347, 42356.99, TRUE, "mixed isotope values?") %>% #20200804 #IAEA-C2 looks like eSSB instead of C2 values in 18O and 13C
#   change.donotuse.and.runinfo(42357, 42366.99, TRUE, "stir stick thrown") %>% #20200804 #ETH1, computer communication error
#   change.donotuse.and.runinfo(42417, 42420.99, TRUE, "high initial yield. not all CO2?") %>% #20200805 #dR_25, 122 mbar initial volume. but then compressed to 6% to get 16V - did He get in there?
#   #change.donotuse.and.runinfo(42466, 42475.99, TRUE, "stir stick thrown") #20200806 #IAEA-C2, thrown stir stick
#   change.donotuse.and.runinfo(42570, 42570.99, TRUE, "cullinng 11th acquisitions") %>% #20200807 #ETH3, 11 acqs accidently 
#   change.donotuse.and.runinfo(42636, 42639.99, TRUE, "low m44 voltages, very high initial bellows reading") %>% #20200809 #dR_25, very high initial bellows reading (~112mbar) but only 10V of CO2. 
#   change.donotuse.and.runinfo(42755, 42766.99, TRUE, "eSSB_25, way colder than rest of pop in D47") %>% #20200811  #eSSB_25
#   change.donotuse.and.runinfo(42792, 42801.99, TRUE, "ETH2 far fromr rest of reps in bulk isos") %>%  #20200811 #ETH2 different in bulk isos
#   change.donotuse.and.runinfo(42802, 42811.99, TRUE, "thrown stick?")  %>%  #20200811 #IAEA-C1, far off in bulk isos
#   change.donotuse.and.runinfo(42812, 42821.99, TRUE, "ETH2 far fromr rest of reps in bulk isos")  %>%  #20200811 #ETH2 far fromr rest of reps in bulk isos
#   #change.donotuse.and.runinfo(42933, 42942.99, TRUE, "diff in bulk isos")  %>%  #20200813 #ETH2 far off in bulk isos
#   change.donotuse.and.runinfo(43549, 43558.99, TRUE, "not enough gas")  %>%  #20200821 #TS3-16-20 not enough gas, low wt % carb
#   change.donotuse.and.runinfo(43679, 43680.99, TRUE, "not enough gas") %>%   #20200823 #TS3-16-02, not enough gas
#   change.donotuse.and.runinfo(43767, 43768.99, TRUE, "not enough gas")  %>%  #20200825 #TS3-16-20 not enough gas, low wt % carb
#   change.donotuse.and.runinfo(43880, 43883.99, TRUE, "zeros offset in D47 space") %>%  #20200827 #zeros far from pop in D47vd47
#   change.donotuse.and.runinfo(43894, 43903.99, TRUE, "ETH2 far fromr rest of reps in bulk isos")  %>%  #20200827  
#   change.donotuse.and.runinfo(43904, 43913.99, TRUE, "eSSB_1000 very different from rest of pop in D47d47") %>%  #20200827 #eSSB_1000 very diff in D47 and d47 space
#   change.donotuse.and.runinfo(43937, 43946.99, TRUE, "dR_25 far from pop in D47vd47") %>%  #20200828 #dR_25 far from pop in D47vd47
#   change.donotuse.and.runinfo(44157, 44166.99, TRUE, "eSSB_1000 far from pop in d18Ovd13C space") %>% #20200831 #eSSB_1000 far from pop in d18Ovd13C space
#   change.donotuse.and.runinfo(44187, 44196.99, TRUE, "TS3-16-20.gen2") %>%  #20200831 #low voltages, never reached 16V 
#   change.donotuse.and.runinfo(44257, 44266.99, TRUE, "ETH1 far from rest of pop in single iso  and clumped space") %>% #20200901 #ETH1 far from pop in all isotopes
#   change.donotuse.and.runinfo(44538, 44547.99, TRUE, "eSSB_1000 far from pop in D47d47 space") #20200907 #eSSB_1000 far from pop in D47d47 space
# 
# #renaming
# flatlist.Cyc[  flatlist.Cyc$Analysis > 44317 & flatlist.Cyc$Analysis < 44326.99, "Identifier 1"] <- "ACF$AF-NCF-TS3-16-15" #20200902 #fixing TS3-16-15 naming issue
# flatlist.Cyc[  flatlist.Cyc$Analysis > 44457 & flatlist.Cyc$Analysis < 44466.99, "Identifier 1"] <- "JOV$SPB19-ML59-A"  #20200904 #fixing JOV naming issue
# flatlist.Cyc[  flatlist.Cyc$Analysis > 44467 & flatlist.Cyc$Analysis < 44476.99, "Identifier 1"] <- "JOV$SPB19-ML60-A"  #20200904 #fixing JOV naming issue
# flatlist.Cyc[  flatlist.Cyc$Analysis > 44497 & flatlist.Cyc$Analysis < 44505.99, "Identifier 1"] <- "JOV$SPB19-ML63-B"  #20200904 #fixing JOV naming issue
# flatlist.Cyc[  flatlist.Cyc$Analysis > 44507 & flatlist.Cyc$Analysis < 44516.99, "Identifier 1"] <- "JOV$SPB19-ML64-A"  #20200904 #fixing JOV naming issue
```

### 38838 to 41786 - ACF - AF9

User <- "ACF"

session <-"AF9"

session_date_start <- 20200505

session_date_end <- 20200716

session_analysis_start <- 38838

session_analysis_end <- 41786

```{r 38838 to 41786 - ACF - AF9}
# #TEMPLATE for AF9 session
# #flatlist.Cyc <- flatlist.Cyc %>% change.donotuse.and.runinfo(#####, #####.99, TRUE, "COMMMENT") #DATE #FURTHER NOTES
# 
# #marking "Donotuse" or adding comment
# flatlist.Cyc <- flatlist.Cyc %>%
#    change.donotuse.and.runinfo(38779, 38790.99, TRUE, "far away from pop. in D47vd47 space") %>% #05/05/2020 #dR_25 , batch 2
#    change.donotuse.and.runinfo(38813, 38824.99, TRUE, "far away from pop. in D47vd47 space") %>% #05/05/2020 #dR_25, batch 5
#    change.donotuse.and.runinfo(38791, 38803.99, TRUE, "far away from pop. in D47vd47 space") %>% #05/05/2020 #ETH1. batch 3
#    change.donotuse.and.runinfo(38956,38968.99,TRUE,"offset from other dR_25 in D47vd47") %>% #05/13/2020 #dR_25 offset from rest of pop in D47vd47 space and is rotating the D48 transfer function
#    change.donotuse.and.runinfo(39124,39133.99,TRUE,"offset from other dR_25 in D47vd47") %>% #06/08/2020: dR_25 offset from rest of population in D47vd47 space in particular
#    change.donotuse.and.runinfo(39214,39223.99,FALSE,"flagged as maybe D48excess") %>% #06/08/2020: ETH2 flagged as maybe D48excess in P2 of data reduction
#    change.donotuse.and.runinfo(39234,39243.99,TRUE,"not enough gas") %>%#06/10/2020: CU Yule had low gas to start with, never got to 16V in run, do not use
#    change.donotuse.and.runinfo(39268,39299,TRUE,"dropbox error: remnant") #during day 06/11/2020: carousel did drop so no carbs ran after Batch 44 (all$eSSB_25), so ETH2,2,1,3 are all remnant gases from eSSB_25 -- do not use. rename them all and then label Donotuse #ETH2,2,1,3 batch 39: flagging bc pressures slightly lower than 16000mV
#   change.donotuse.and.runinfo(39382, 39392.99, FALSE, "offset in D47vd47 space from rest") %>%  #06/12/2020: dR_1000 falling off of rest of replicates. flagged on 06/18/2020 
#   change.donotuse.and.runinfo(39332, 39341.99, TRUE, "no peak center, background, pressure balance") %>% #was labeled in sequence ETH2 (9.3 mg), needs to be CU YULE (10.3)
#   change.donotuse.and.runinfo(39342, 39351.99, TRUE, "no peak center, background, pressure balance") %>% #was labeled ETH2 (8.9 mg) in sequence, needs to be ETH2 (9.3mg)
#   change.donotuse.and.runinfo(39352, 39361.99, TRUE, "no peak center, background, pressure balance") %>% #was labeled ETH1 (12.0mg) in sequence, needs to be ETh2 (8.9mg)
#   change.donotuse.and.runinfo(39362, 39371.99, TRUE, "no peak center, background, pressure balance") %>% #was labeled ETH1 (9.9) in sequence, needs to be labeled ETH1 (12.0mg)
#   change.donotuse.and.runinfo(39372, 39381.99, TRUE, "no peak center, background, pressure balance") %>% #was labeled ETH3 (10.2) in sequence, needs to be labeled ETH1 (9.9mg)
#   change.donotuse.and.runinfo(39523, 39546.99, TRUE, "possible thrown stir stick ") %>%  #zeros ran at 17000mV. adjusted the delay on the refill method from 50s to 40s and that seemed to get the zeros to run around 16000mV
# #stir stick found not spinning Monday AM 06/15/2020. not sure when between Friday at 12pm and Monday 8:00am it stopped, marking the standards that ran over the weekend as 'possible thrown stir stick ' to flag but not throw out yet.
#   change.donotuse.and.runinfo(39393, 39402.99, FALSE, "possible thrown stir stick ") %>%  #all$ETH3, 10.2mg
#   change.donotuse.and.runinfo(39403, 39412.99, FALSE, "possible thrown stir stick ") %>%  #all$CU YULE	9.4
#   change.donotuse.and.runinfo(39413, 39422.99, FALSE, "possible thrown stir stick ") %>%  #all$ETH1	9.6
#   change.donotuse.and.runinfo(39423, 39432.99, FALSE, "possible thrown stir stick ") %>%  #all$ETH2	11.3
#   change.donotuse.and.runinfo(39433, 39442.99, FALSE, "possible thrown stir stick ") %>%  #all$ETH3	9
#   change.donotuse.and.runinfo(39443, 39452.99, FALSE, "possible thrown stir stick ") %>%  #all$CU YULE	11.3
#   change.donotuse.and.runinfo(39453, 39462.99, FALSE, "possible thrown stir stick ") %>%  #all$ETH1	13
#   change.donotuse.and.runinfo(39463, 39472.99, FALSE, "possible thrown stir stick ") %>%  #all$ETH2	10.5
#   change.donotuse.and.runinfo(39473, 39482.99, FALSE, "possible thrown stir stick ") %>%  #all$ETH3	9.4
#   change.donotuse.and.runinfo(39483, 39492.99, FALSE, "possible thrown stir stick ") %>%  #all$CU YULE	9.1
#   change.donotuse.and.runinfo(39493, 39502.99, FALSE, "possible thrown stir stick ") %>%  #all$ETH1	10.5
#   change.donotuse.and.runinfo(39503, 39512.99, FALSE, "possible thrown stir stick ") %>%  #all$ETH2	8.2
#   change.donotuse.and.runinfo(39513, 39522.99, TRUE, "only 9 Acq, mistake. and possible thrown stir stick ") %>%  #all$ETH3	9.4
#   change.donotuse.and.runinfo(39687, 39690.99, TRUE, "only single shot of eSSB_25 bottle. not enough gas") %>% #only single shot of eSSB_25 bottle. not enough gas
#   change.donotuse.and.runinfo(39963, 39967.99, TRUE, "TS2-16-05, not enough gas, 9.35mg") %>% #06/20/2020: AF-NCF-TS2-16-05. not enough gas
#   change.donotuse.and.runinfo(40373, 40382.99, TRUE, "sample id unknown. cull") %>%   #06/26/2020
#   change.donotuse.and.runinfo(40473, 40482.99, TRUE, "TS3-16-19, not enough gas, 9.22mg") %>%   #06/27/2020
#   change.donotuse.and.runinfo(40513, 40522.99, TRUE, "TS3-16-19, not enough gas, 11.39mg") %>%  #06/28/2020
#   change.donotuse.and.runinfo(40703, 40712.99, FALSE, "possible thrown stir stick") %>%   #07/01/2020 #ETH2 9.56mg
#   change.donotuse.and.runinfo(40713, 40722.99, FALSE, "possible thrown stir stick") %>%  #07/01/2020 #ACF$AF-NCF-TS2-16-02 11.22mg
#   change.donotuse.and.runinfo(40733, 40742.99, FALSE, "possible thrown stir stick") %>%   #07/01/2020#ACF$AF-NCF-TS2-16-17 8.54mg
#   change.donotuse.and.runinfo(40743, 40752.99, TRUE, "possible thrown stir stick") %>%   #07/01/2020 #ETH1 9.06mg
#   change.donotuse.and.runinfo(39184,39193.99,TRUE,"low gas, below 16V") #07/01/2020 #dR_1000, Batch 36: not labelling as donotuse yet, but flagging
#   change.donotuse.and.runinfo(39299,39310.99,TRUE,"funky zeros, maybe zero gas and eSSB_25 mixed?") %>% #07/01/2020
#   change.donotuse.and.runinfo(	39433,39442.99,FALSE,"low gas, most Acq's below 16V")#07/01/2020 
# 
# #renaming
#   flatlist.Cyc[  flatlist.Cyc$Analysis > 38779 & flatlist.Cyc$Analysis < 38790.99, "Identifier 1"] <- "all$zero"  #no gas was transferred ran zero from before
#   flatlist.Cyc[  flatlist.Cyc$Analysis > 38791 & flatlist.Cyc$Analysis < 38803.99, "Identifier 1"] <- "all$zero"  #no gas was transferred ran zero from before
#   flatlist.Cyc[  flatlist.Cyc$Analysis > 39268 & flatlist.Cyc$Analysis < 39299, "Identifier 1"] <- "all$eSSB_25"  #during day 06/11/2020: carousel did drop so no carbs ran after Batch 44 (all$eSSB_25), so ETH2,2,1,3 are all remnant gases from eSSB_25 -- do not use. rename them all and then label Donotuse
#   flatlist.Cyc[  flatlist.Cyc$Analysis > 39312 & flatlist.Cyc$Analysis < 39322, "Identifier 1"] <- "all$dR_1000"  
#   #flatlist.Cyc[  flatlist.Cyc$Analysis > 39717 & flatlist.Cyc$Analysis < 39726.99, "Identifier 1"] <- "ACF$AF-NCF-TS3-16-10" #06/16/2020
#   flatlist.Cyc[  flatlist.Cyc$Analysis > 39332 & flatlist.Cyc$Analysis < 39341.99, "Identifier 1"] <- "all$CU YULE" #was labeled in sequence ETH2 (9.3 mg), needs to be CU YULE (10.3)
#   flatlist.Cyc[  flatlist.Cyc$Analysis > 39332 & flatlist.Cyc$Analysis < 39341.99, "Identifier 2"] <- "10.3" #was labeled in sequence ETH2 (9.3 mg), needs to be CU YULE (10.3)
# flatlist.Cyc[  flatlist.Cyc$Analysis > 39342 & flatlist.Cyc$Analysis < 39351.99, "Identifier 1"] <- "all$ETH2" #was labeled ETH2 (8.9 mg) in sequence, needs to be ETH2 (9.3mg)
#   flatlist.Cyc[  flatlist.Cyc$Analysis > 39342 & flatlist.Cyc$Analysis < 39351.99, "Identifier 2"] <- "9.3" #was labeled ETH2 (8.9 mg) in sequence, needs to be ETH2 (9.3mg)
#   flatlist.Cyc[  flatlist.Cyc$Analysis > 39352 & flatlist.Cyc$Analysis < 39361.99, "Identifier 1"] <- "all$ETH2" #was labeled ETH1 (12.0mg) in sequence, needs to be ETh2 (8.9mg) 
#   flatlist.Cyc[  flatlist.Cyc$Analysis > 39352 & flatlist.Cyc$Analysis < 39361.99, "Identifier 2"] <- "8.9" #was labeled ETH1 (12.0mg) in sequence, needs to be ETh2 (8.9mg)
#   flatlist.Cyc[  flatlist.Cyc$Analysis > 39362 & flatlist.Cyc$Analysis < 39371.99, "Identifier 1"] <- "all$ETH1" #was labeled ETH1 (9.9) in sequence, needs to be labeled ETH1 (12.0mg)
#   flatlist.Cyc[  flatlist.Cyc$Analysis > 39362 & flatlist.Cyc$Analysis < 39371.99, "Identifier 2"] <- "12.0" #was labeled ETH1 (9.9) in sequence, needs to be labeled ETH1 (12.0mg)
#   flatlist.Cyc[  flatlist.Cyc$Analysis > 39372 & flatlist.Cyc$Analysis < 39381.99, "Identifier 1"] <- "all$ETH1" #was labeled ETH3 (10.2) in sequence, needs to be labeled ETH1 (9.9mg)
#   flatlist.Cyc[  flatlist.Cyc$Analysis > 39372 & flatlist.Cyc$Analysis < 39381.99, "Identifier 2"] <- "9.9" #was labeled ETH3 (10.2) in sequence, needs to be labeled ETH1 (9.9mg)
#   flatlist.Cyc[  flatlist.Cyc$Analysis > 40032 & flatlist.Cyc$Analysis < 40041.99, "Preparation"] <- "X" #06/21/2020: relabelling dR_1000 with Preparation = X
#   flatlist.Cyc[  flatlist.Cyc$Analysis > 40523 & flatlist.Cyc$Analysis < 40532.99, "Identifier 1"] <- "JOV$SPB19-ML33-AB"  #06/28/2020
#   flatlist.Cyc[  flatlist.Cyc$Analysis > 40823 & flatlist.Cyc$Analysis < 40832.99, "Identifier 1"] <- "all$eSSB_1000"  #07/03/2020
```

### 30339 to 33637 - ACF - AF8

User <- "ACF"

session <-"AF8"

session_date_start <- 20190702 (included data from previous runs in data reduction bc steady ref frame)

session_date_end <- 20190716

session_analysis_start <- 31489

session_analysis_end <- 33637

```{r 30339 to 33637 - ACF - "AF8"}
# 
# #pulled from May and June, name fixes from katie -> May 2019
# flatlist.Cyc[  flatlist.Cyc$Analysis > 29557 & flatlist.Cyc$Analysis < 29565.8, "Identifier 1"] <- "all$CU YULE"
# flatlist.Cyc[  flatlist.Cyc$Analysis > 30223 & flatlist.Cyc$Analysis < 30231.8, "Identifier 1"] <- "Rehmus$Pin 178.36"
# flatlist.Cyc[  flatlist.Cyc$Analysis > 30356 & flatlist.Cyc$Analysis < 30361.8, "Identifier 1"] <- "all$dR_25"
# flatlist.Cyc[  flatlist.Cyc$Analysis > 30765 & flatlist.Cyc$Analysis < 30773.8, "Identifier 1"] <- "all$eSSB_25"
# flatlist.Cyc[  flatlist.Cyc$Analysis > 30449 & flatlist.Cyc$Analysis < 30457.8, "Identifier 1"] <- "all$eSSB_1000"
# flatlist.Cyc[  flatlist.Cyc$`Identifier 1` == "all$Merk", "Identifier 1"] <- "all$Merck"
# flatlist.Cyc[  flatlist.Cyc$Analysis > 31836 & flatlist.Cyc$Analysis < 31844.8, "Identifier 1"] <- "ACF$AF-NCF-TS2-16-26"  #sequence error where i forgot a normalrun_start caused the carousel  to get behind by one compared to the sequence labelling.so AF-NCF-TS2-16-26 was mislabeled as AF-NCF-TS2-16-24
# flatlist.Cyc[  flatlist.Cyc$Analysis > 31980 & flatlist.Cyc$Analysis < 31988.8, "Identifier 1"] <- "ACF$AF-NCF-TS2-16-22"
# flatlist.Cyc[  flatlist.Cyc$Analysis > 31989 & flatlist.Cyc$Analysis < 31997.8, "Identifier 1"] <- "ACF$AF-NCF-TS2-16-12"
# 
# #getting metadata
# flatlist.Cyc <- flatlist.Cyc %>% 
#   getmetadatafromAnalysis(29988,29991.8,29979) %>% 
#   getmetadatafromAnalysis(29988,29991.8,29979) %>% 
#   getmetadatafromAnalysis(29979,29987.8,29970) %>% 
#   getmetadatafromAnalysis(29970,29978.8,29961) %>% 
#   getmetadatafromAnalysis(29961,29969.8,29952) %>% 
#   getmetadatafromAnalysis(29952,29960.8,29943) %>% 
#   getmetadatafromAnalysis(29943,29951.8,29934) %>% 
#   getmetadatafromAnalysis(29934,29942.8,29929) %>% 
#   getmetadatafromAnalysis(29929,29933.8,29928) %>% 
#   getmetadatafromAnalysis(30356,30361.8,30357) %>%#miss labeled
#   getmetadatafromAnalysis(30999,31007.8,30990) %>%
#   getmetadatafromAnalysis(30990,30998.8,30981) %>%
#   getmetadatafromAnalysis(30981,30989.8,30972) %>%
#   getmetadatafromAnalysis(30972,30980.8,30963)
# 
# ## 07/18/2019.... poweroutage at 7:34AM. ACF$Af-NCF-TS2-21.5Bspar-gen2 2.769 shouldbe fine, but lost 6 samples after that do to carousel glitches
# 
# #flatlist.Cyc <- flatlist.Cyc %>%
#  #change.donotuse.and.comment(30963,30971.8,FALSE,"This sample was missing from the seq and needing the next samples to be pushed down") %>%
#  #change.donotuse.and.comment(31127,31135.8,TRUE,"This EHT1 is a outlier, we don't know why") %>%
#  #change.donotuse.and.comment(31181,31189.8,TRUE,"This EHT2 is a outlier, we don't know why")
# 
# ##NOTE: Marina Suerez and Dusin Harper from KU ran between 07/08/2019-07/13/2019, then i jumped back on the 253. Reference frame looks contintously stable so keeping ref frame.
# 
# #note that when using Analysis numbers from the flatlist.Cyc dataframe, the analyses include .1 to .7 at the end of each number. So, you need to account for that when defining the ranges. The function is set to read <= and >= for the upper and lower bounds, respectively.
# 
# flatlist.Cyc <- flatlist.Cyc %>%
#   change.donotuse.and.runinfo(31392,31396,TRUE,"less then 12.5V") %>%  #dR_1000
#   change.donotuse.and.runinfo(31612,31621,FALSE,"stir stick maybe thrown. monitor against further replicates") %>% #ACF$AF-NCF-TS2-16-03
#   change.donotuse.and.runinfo(31621,31630,FALSE,"stir stick maybe thrown. monitor against further replicates") %>% #ACF$AF-NCF-TS2-16-12
#   change.donotuse.and.runinfo(31630,31638,FALSE,"stir stick maybe thrown. monitor against further replicates") %>% #all$ETH1
#   change.donotuse.and.runinfo(31639,31648,FALSE,"stir stick maybe thrown. monitor against further replicates") %>% #ACF$AF-NCF-TS2-16-14
#   change.donotuse.and.runinfo(31648,31657,FALSE,"stir stick maybe thrown. monitor against further replicates") %>% #ACF$AF-NCF-TS2-16-22
#   change.donotuse.and.runinfo(31708.1,31708.4,TRUE,"zero was cut short") %>% #zero was cut short
#   change.donotuse.and.runinfo(31827.1,31836, TRUE, "not enough and sequence error, no gas dropped so this sample just ran previous sample's gas") %>%
#   change.donotuse.and.runinfo(31827.1, 31836, TRUE, "low yield, less than 12.5V") %>%
#   change.donotuse.and.runinfo(31908.1, 31917, TRUE, "low yield, less than 12.5V") %>%
#   change.donotuse.and.runinfo(29625.1,29633.7,TRUE,"offset from the rest of population of dR_25, keep eye on")%>%
#   change.donotuse.and.runinfo(32136.1,32136.7,TRUE,"low yield") %>%
#   change.donotuse.and.runinfo(32853, 32862, TRUE, "low yield, weigh out more next time") %>%  #ACF$AF-NCF-TS2-16-10 4.226mg 07/16/2019
#   change.donotuse.and.runinfo(33244, 33253, TRUE, "low yield, stir stick issue") %>% #all$ETH3 8.132mg 07/21/2019, stir stick blown
#   change.donotuse.and.runinfo(33253, 33262, TRUE, "low yield, stir stick issue") %>% #ACF$AF-NCF-TS3-16-01 6.016mg 07/21/2019, stir stick blown
#   change.donotuse.and.runinfo(33306, 33315, TRUE, "low yield, come gas pumped away bc of compressed air issue w/ valve8") %>% #ACF$AF-NCF-TS3-16-15 8.123mg 07/22/2019
#   change.donotuse.and.runinfo(33315, 33324, FALSE, "cryocooler off, watch for d18O issues") %>% #ACF$AF-NCF-TS3-16-01 7.629mg 07/22/2019, cryocooler off
#   change.donotuse.and.runinfo(33324, 33333, TRUE, "cryocooler off, watch for d18O issues") %>% #all$ETH1 4.916mg 07/22/2019, cryocooler off
#   change.donotuse.and.runinfo(33333, 33342, TRUE, "cryocooler off, watch for d18O issues") %>%  #ACF$AF-NCF-TS3-16-15 6.972 07/22/2019, cryocooler off. cryowarmed too much for next sample to run.
#   change.donotuse.and.runinfo(33370,33378, TRUE, "not enough gas, less than 12.5mV") %>% #AF-NCF-TS3-16-19
#   change.donotuse.and.runinfo(33406,33415, TRUE, "not enough gas, less than 12.5 mV") %>%  #AF-NCF-TS3-16-01
#   change.donotuse.and.runinfo(29625.1, 29633.7,TRUE,"offset from the rest of population of dR_25, keep eye on") %>% #maybe throw out if later in clumped processing this sample varies in D47 space greatly
#   change.donotuse.and.runinfo(30963.1, 30972,TRUE,"bulk isotopes offset from the rest of population of ETH1") %>%
#   change.donotuse.and.runinfo(31181.1, 31190.1,TRUE,"bulk isotopes offset from the rest of population of ETH2") %>%
#   change.donotuse.and.runinfo(31392.1, 31397.1, TRUE, "sample too small") %>%
#   change.donotuse.and.runinfo(31585.1, 31594.1, FALSE, "sample sat in trap 2 for ~60 mins bc of a FromPy read error between computers, keep an eye one")  %>%
#   #looking at the D47vsd47 plot, it appears to fall on top of all the other dR_25 and is not labelled at D48excess... I'd keep for now
#   change.donotuse.and.runinfo(31127.1, 31136.1, TRUE, "bulk isotopes offset from the rest of population of ETH1") %>%
#   change.donotuse.and.runinfo(29378.1, 29383, TRUE, "bulk isotopes offset from rest of populations of ETH2") %>%
#   change.donotuse.and.runinfo(30341.1, 30362, TRUE, "unexplained long strain fo dR_25 and then 5 eSSB_25") %>%  #dR_25 odd
#   change.donotuse.and.runinfo(29255.1, 29264, TRUE, "dR_25 offset from rest of pop in bulk iso") %>%
#   change.donotuse.and.runinfo(31809.1, 31818, FALSE,"ETH2 offset from rest of population. keep eye one") %>%
# #after looking at standard residuals for ETHs and identifying outliers that I am a fence about culling
#   change.donotuse.and.runinfo(29369.1,29378, TRUE, "ETH1 outlier from rest of population") %>% #i think keep
#   change.donotuse.and.runinfo(31809.1,31818, TRUE, "ETH2 outlier from rest of population") %>% #i think cull
#   change.donotuse.and.runinfo(30895.1,30904, FALSE, "ETH3 high positive outlier from rest of population") %>% #batch 127. i think keep
#   change.donotuse.and.runinfo(30250.1,30259, FALSE, "ETH3 high positive outlier from rest of population") %>% #batch 81. i think keep
#   change.donotuse.and.runinfo(29351.1,29360, TRUE, "ETH3 negative outlier from rest of population") %>%  #from 20150520. batch 28. i think cull
#   change.donotuse.and.runinfo(29652.1,29661, TRUE, "ETH3 negative outlier from rest of population") %>%  #from 20190524. batch 50. i think cull
#   change.donotuse.and.runinfo(32745.1,32753.7, TRUE, "ETH3 very positive compared to rest of population" ) %>% #from 20190715. i think cull
#   change.donotuse.and.runinfo(32754.1, 32762.7, TRUE, "offest from rest of pop of ETh1 by a lot") %>%
#   change.donotuse.and.runinfo(32853.1, 32861.7, TRUE, "maybe not enough gas? only 10.8 but ran ") %>%
#   change.donotuse.and.runinfo(32862.1, 32870.7, FALSE, "first d18O cycles are off from average. want to wait to see if this rep falls away from rest of pop") %>%  #ETH2 7.725
#   change.donotuse.and.runinfo(32871.1, 32879.7, FALSE, "first d18O cycles are off from average. want to wait to see if this rep falls away from rest of pop") %>%  #AF-NCF-TS2-16-28
#   change.donotuse.and.runinfo(33213.1, 33213.9, TRUE, "test of computer communication") %>%
#   change.donotuse.and.runinfo(33214.1, 33214.9, TRUE, "test of computer communication") %>%
#   change.donotuse.and.runinfo(30678,30686, TRUE, "falls out of cluster in both D47 and d47 space") %>%
#   change.donotuse.and.runinfo(33370.1,33378.9, TRUE, "not enough gas") %>%
#     #added 20191118
#   change.donotuse.and.runinfo(30125.1, 30132.9, TRUE, "falls out of cluster in d18Ovd13C space") %>%  #dR_1000 batch 97 07/01/2019
#   change.donotuse.and.runinfo(32943.1, 32943.4, TRUE, "four cycles fall outside of cluster obviously") %>%  #AF-NCF-TS2-16-10
#   change.donotuse.and.runinfo(31055.1, 31062.7, TRUE, "offset from rest of replicates") %>%  #eSSB_25
#   change.donotuse.and.runinfo(30133.1, 30133.7, TRUE, "7 cycles that are not associated with full run") %>% #ETH1
#   change.donotuse.and.runinfo(33217.1, 33225.7, TRUE, "offset from the rest of large population") %>% #ETH1
#   change.donotuse.and.runinfo(32862.1, 32870.7, TRUE, "offset from rest of population") %>% #ETH2
#   change.donotuse.and.runinfo(30051.1, 30059.7, TRUE, "offset from rest of population") %>% #ETH2 (could also consider culing batch 444, 98, 70)
#   change.donotuse.and.runinfo(33279.1, 33287.7, TRUE, "offset from rest of population") %>% #eSSB_1000
#   change.donotuse.and.runinfo(29844.1, 29852.7, TRUE, "offset from rest of population") %>% #eSSB_1000
#   change.donotuse.and.runinfo(33226.1, 33234.7, TRUE, "offset from rest of population") %>% #IAEA-C2
#   change.donotuse.and.runinfo(30125.1, 30133.7, TRUE, "offset from ETH1 group looking at std residuals") %>%  #ETH1, 30133, 97
#   change.donotuse.and.runinfo(33397.1, 33405.7, TRUE, "offset from ETH1 group looking at std residuals") %>%  #ETH1, 33397, 437
#   change.donotuse.and.runinfo(33599.1, 33607.7, TRUE, "offset from the population when looking at the Std residuals in clumped code") %>%   #ETH2, 33599, 459
#   change.donotuse.and.runinfo(29979.1, 29987.7, TRUE, "isodat readin error, no ID1 or mass or prep for no reason")
# 
# #95: dR_1000: first few cucles fall outside of 1sgima in d18O (positive, by max 0.04)
# #238: dR_1000. not enough gas, too few cycles for complete sample . looking at ind plots, looks like there is a weak linear relationship in both d13C and d18O overtime
# #242: Cu YULE. first few cycles fall outside of the 1sigma in d18O (positive, by max .08).
# #251: dR_25. first few cycles fall outside of the 1sigma in d18O (positive, by max .04)
# #269: zero. cut short zero
# #272: three outliers at the beginning of run all out of 2sigma. little noisy, but going to keep in data for now
# #290: 4 outliers
# #290: first three cycles are outliers in d18O compared to the rest of the pop
# #308: gap in analysis number
# #372: ETH1. outliers in first Acq in d18O
# #373: AF-NCF-TS2-16-21.5Bspar-gen2. outliers in d18O also
# #382: first few cycles in d18O are outliers but fall into place with the average by the 7th cycle .... AF-NCF-TS-17-ElyLS
# #384: first few cycles in d18O are outliers but fall into place with the average by the 7th cycle .... ETH2, 32862.1 to 32870.7
# #385: same tail behavior at 384, by 6 cycles d18O comes back into line with average ... AF-NCF-TS2-16-28, 32871.1 to 32879.7
# #393: first few cycles in d18O are outliers but fall into place with average by 7th cycle ... AF-NCF-TS2-16-10
```


### 23838 to 24446- ACF - AF7_Canary Islands

User <- ACF

session <- AF7

session_date_start <- 20190214

session_date_end <- 20200214

session_analysis_start <- 23838

session_analysis_end <- 24446

```{r Data correction info - 23838 to 24446- ACF - AF7}

# Running Canary Island travertines for Dr. Ana Maria Alonso-Zarza at the Universidad Complutense de Madrid. Run session from 02/14/2019 to 02/28/2019. 
# This data is a preliminary dataset for Dr. Alonso-Zarza. The 253 mass spectrometer is working but not producing data with the precision we would ultimately like.  This data provides an intial look at the stable ad clumped isotope values and temperatures, and will be compared with later data replicates that will be produced once remaining machine issues are resolved. 
# 
# Samples | Weight (mg) | %CaCo (XRD)
# --------|-------------|------------
# AZ-16   | 122         | 95
# AZU6-1  | 26          | 94
# AZ-13A  | 328         | 95
# PRE-6   | 25          | 100
# PRE-9   | 37          | 100
# HOR-1   | 69          | 100
# HOR-6   | 137         | 100
# 
# #renaming 
# flatlist.Cyc[ flatlist.Cyc$'Identifier 1' == "ACF$HOR-16" , "Identifier 1"] <- "ACF$HOR-6"
# flatlist.Cyc[  flatlist.Cyc$Analysis > 24312 & flatlist.Cyc$Analysis < 24321, "Identifier 1"] <- "all$eSSB_1000" #mislabeled as eSSB2_25
# flatlist.Cyc[  flatlist.Cyc$Analysis > 23849 & flatlist.Cyc$Analysis < 23858, "Identifier 1"] <- "all$eSSB_25" #removing "2" from name to match other gases
# flatlist.Cyc[  flatlist.Cyc$Analysis > 23867 & flatlist.Cyc$Analysis < 23876, "Identifier 1"] <- "all$eSSB_25"  #removing "2" from name to match other gases
# flatlist.Cyc[  flatlist.Cyc$Analysis > 24366 & flatlist.Cyc$Analysis < 24375, "Identifier 1"] <- "ACF$AZU6-1"  #AZU6-1 mislabeled as ETH1 (AZU6-1 ran first)
# flatlist.Cyc[  flatlist.Cyc$Analysis > 24375 & flatlist.Cyc$Analysis < 24384, "Identifier 1"] <- "all$ETH1"  #ETH1 mislabeled as AZU6-1 (ETH1 ran second)
# 
# flatlist.Cyc <- flatlist.Cyc %>% 
#   mutate(Donotuse = ifelse(Analysis > 24164 & Analysis < 24176, TRUE, FALSE))
# 
# #water trap was warm for full day on 02/18/2019. below labelling notes this error
# flatlist.Cyc <- flatlist.Cyc %>% 
#   mutate(runinfo = ifelse(Analysis > 24146 & Analysis < 24156, "ran warm water trap, use replicate thoughtfully", 
#                           ifelse(Analysis > 24155 & Analysis < 24165, "ran warm water trap, use replicate thoughtfully", 
#                                  ifelse(Analysis > 24164 & Analysis < 24176, "Do not use. 11 acq, and large d18O std dev. ran warm water trap, use replicate thoughtfully",
#                                          ifelse(Analysis > 24175 & Analysis < 24185, "ran warm water trap, use replicate thoughtfully", 
#                                                 ifelse(Analysis > 24184 & Analysis < 24194, "ran warm water trap, use replicate thoughtfully", 
#                                                        ifelse(Analysis > 24201 & Analysis < 24212, "ran warm water trap, use replicate thoughtfully",
#                                                                ifelse(Analysis > 24211 & Analysis < 24221, "ran warm water trap, use replicate thoughtfully",
#                                                                                                                                                    ""))))))))
# #####Subsetting to get data from 02/18 02/21/2019}
# #whole day ran with a warm water trap (02/18), so I ran the same suite of samples on 02/19 with a cold water trap
# #need to compare the data and see if 02/18 data are usable replicates, so copying plots from above
# 
# flatlist.Cyc_0218to0221 <- flatlist.Cyc %>% filter(Analysis > 24147 & Analysis < 24446 ) 
# 
# combined_data_acquisition_0218to0221 <- combined_data_acquisition %>% filter(Analysis > 24147 & Analysis < 24446 )
# 
# 
# Samples | Weight (mg) | %CaCo (XRD) | Replicates|        | Notes
# --------|-------------|-------------|-----------|--------|------------------------------------------------
#         |             |             |           | Attempted | Usable    
# AZ-16   | 122         | 95          | 2         | 2      | all clean on both 1000C and 25C D48excess
# AZU6-1  | 26          | 94          | 3         | 2      |all with 1000C D48excess but not 25C D48excess
# AZ-13A  | 328         | 95          | 2         | 2      | all clean on both 1000C and 25C D48excess
# PRE-6   | 25          | 100         | 3         | 2      |1 with both D48excess, 1 with 1000C but not 25C
# PRE-9   | 37          | 100         | 3         | 3      |all clean on both 1000C and 25C D48excess
# HOR-1   | 69          | 100         | 2         | 0      | all with both 1000C and 25C excess
# HOR-6   | 137         | 100         | 2         | 2      | all clean on both 1000C and 25C D48excess

```

### 15027 to 15734 - ACF - AF6

User <- ACF 

session <- AF6

session_date_start <- 20180618

session_date_end <- 20180627

session_analysis_start <- 15027

session_analysis_end <- 15734

```{r Data correction info - 15027 to 15734 - ACF - AF6}

#"Raw Data Processing to CIDS - LIDIvTrad and Knc samples  "
# 
# for (ID in c(15605:15613)){
#   rawdata[ rawdata$Analysis == ID, "Identifier 1"] <- "all$eIB2_1000"
# }
# for (ID in c(15643:15651)){
#   rawdata[ rawdata$Analysis == ID, "Identifier 1"] <- "all$eIB2_1000"
# }
# 
# ##Need to go back and rename adam's Carraras to correct Carrara.CIT
# for (ID in c(15027:15035)){
#   rawdata[ rawdata$Analysis == ID, "Identifier 1"] <- "all$Carrara.CIT"
# }
# 
# for (ID in c(15063:15071)){
#   rawdata[ rawdata$Analysis == ID, "Identifier 1"] <- "all$Carrara.CIT"
# }
# 
# for (ID in c(15265:15273)){
#   rawdata[ rawdata$Analysis == ID, "Identifier 1"] <- "all$Carrara.CIT"
# }
# 
# for (ID in c(15072:15080)){
#   rawdata[ rawdata$Analysis == ID, "Identifier 1"] <- "all$ETH_3"
# }
# 
# for (ID in c(15045:15053)){
#   rawdata[ rawdata$Analysis == ID, "Identifier 1"] <- "all$ETH_3"
# }
# 
# for (ID in c(15184:15192)){
#   rawdata[ rawdata$Analysis == ID, "Identifier 1"] <- "all$eIB2_1000"
# }
```

### 14432 to 14859 - ACF - Canary Islands_1

User <- ACF

session <- Canary Islands_1

session_date_start <- 20180522

session_date_end <- 20180527

session_analysis_start <- 14432

session_analysis_end <- 14859

```{r Data correction info - 14432 to 14859 - ACF - Canary Islands_1}

# for (ID in c(12997:13005)){
#   rawdata[ rawdata$Analysis == ID , "Identifier 1"] <- "all$TV04"
# }
# for (ID in c(13006:13014)){
#   rawdata[ rawdata$Analysis == ID , "Identifier 1"] <- "all$Merck"
# }
# for (ID in c(13015:13023)){
#   rawdata[ rawdata$Analysis == ID , "Identifier 1"] <- "all$CIT Carrara"
# } 
# for (ID in c(13024:13032)){
#   rawdata[ rawdata$Analysis == ID , "Identifier 1"] <- "all$ETH_3"
# }
# for (ID in c(13691:13699)){
#   rawdata[ rawdata$Analysis == ID , "Identifier 1"] <- "all$e1B2_25"
# }
# for (ID in c(13358:13366)){
#   rawdata[ rawdata$Analysis == ID , "Identifier 1"] <- "all$d1B2_1000"
# }
# for (ID in c(12626:12634)){
#   rawdata[ rawdata$Analysis == ID , "Identifier 1"] <- "all$Carrara.CIT"
# }
# for (ID in c(13344:13352)){
#   rawdata[ rawdata$Analysis == ID , "Identifier 1"] <- "all$Carrara.CIT"
# }
# for (ID in c(13973:13981)){
#   rawdata[ rawdata$Analysis == ID, "Identifier 1"] <- "all$ETH_2"
# }
# 
# ##Renaming idenitifer1's from 5/24/2018, didn't advance carousel to proper hole, so all data is offset with label by one
# 
# #CIT Carrara data mislabeled in isodat as TV04
# for (ID in c(14565:14573)){
#   rawdata[ rawdata$Analysis == ID, "Identifier 1"] <- "all$Carrara.CIT"
# }
# 
# #TV04 data mislabeled in isodat as AZ-16A
# for (ID in c(14574:14582)){
#   rawdata[ rawdata$Analysis == ID, "Identifier 1"] <- "all$TV04"
# }
# 
# #AZ-16A data mislabeled in isodat as AZ-13A
# for (ID in c(14583:14591)){
#   rawdata[ rawdata$Analysis == ID, "Identifier 1"] <- "ACF$AZ-16A"
# }
# 
# # AZ-13A data mislabeled in isodat as POZ-11
# for (ID in c(14592:14600)){
#   rawdata[ rawdata$Analysis == ID, "Identifier 1"] <- "ACF$AZ-13A"
# }
# 
# #POZ-11 data mislabeled in isodat as AZU6-1
# for (ID in c(14601:14609)){
#   rawdata[ rawdata$Analysis == ID, "Identifier 1"] <- "ACF$POZ-11"
# }
# 
# #AZU6-1 not run

```

### 12626 to 14017- ACF - LTD_1

User <- ACF

session <- LTD_1

session_date_start <- 20180410

session_date_end <- 20200502

session_analysis_start <- 12626

session_analysis_end <- 14017

```{r Data correction info - 12626 to 14017- ACF - LTD_1}

# for (ID in c(12997:13005)){
#   rawdata[ rawdata$Analysis == ID , "Identifier 1"] <- "all$TV04"
# }
# for (ID in c(13006:13014)){
#   rawdata[ rawdata$Analysis == ID , "Identifier 1"] <- "all$Merck"
# }
# for (ID in c(13015:13023)){
#   rawdata[ rawdata$Analysis == ID , "Identifier 1"] <- "all$CIT Carrara"
# } 
# for (ID in c(13024:13032)){
#   rawdata[ rawdata$Analysis == ID , "Identifier 1"] <- "all$ETH_3"
# }
# for (ID in c(13691:13699)){
#   rawdata[ rawdata$Analysis == ID , "Identifier 1"] <- "all$e1B2_25"
# }
# for (ID in c(13358:13366)){
#   rawdata[ rawdata$Analysis == ID , "Identifier 1"] <- "all$d1B2_1000"
# }
# for (ID in c(12626:12634)){
#   rawdata[ rawdata$Analysis == ID , "Identifier 1"] <- "all$Carrara.CIT"
# }
# for (ID in c(13344:13352)){
#   rawdata[ rawdata$Analysis == ID , "Identifier 1"] <- "all$Carrara.CIT"
# }
# for (ID in c(13973:13981)){
#   rawdata[ rawdata$Analysis == ID, "Identifier 1"] <- "all$ETH_2"
# }  
#   
#   rawdata_filtered <- subset(rawdata, v44.mV >10000)
#   rawdata_filtered <- subset(rawdata_filtered, Analysis < 17462 | Analysis >17469)
#   #getting rid of the eBB_1000 from 9/15/2018
#   rawdata2<- subset(rawdata_filtered, as.numeric(Analysis) < 17534  | as.numeric(Analysis) > 17542)
#   
#   flatlist.Cyc <- clumpedbyCycfixref(rawdata2)
#   combined_data_acquisition <- clumpedCyctoAcquisition(flatlist.Cyc)
#   combined_data_group <- clumpedAcquisitiontoRun(combined_data_acquisition)

```

### 5059 to 6157 - ACF - AF5

User <- ACF

session <- AF5

session_date_start <- 20170705

session_date_end <- 20170724

session_analysis_start <- 5059

session_analysis_end <- 6157

```{r Data correction info - 5059 to 6157 - ACF - AF5}

 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5061 & flatlist.Cyc$Analysis < 5069.8, "Identifier 1"] <- "all$Carrara.CIT" #batch 1
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5071 & flatlist.Cyc$Analysis < 5079.8, "Identifier 1"] <- "all$dBBHG" #batch 2
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5080 & flatlist.Cyc$Analysis < 5098.8, "Identifier 1"] <- "all$TV04" #batch 3 
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5089 & flatlist.Cyc$Analysis < 5097.8, "Identifier 1"] <- "all$eYSHG" #batch 4
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5098 & flatlist.Cyc$Analysis < 5106.8, "Identifier 1"] <- "all$NBS19" #batch 5
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5170 & flatlist.Cyc$Analysis < 5178.8, "Identifier 1"] <- "all$eYSEG" #batch 6
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5179 & flatlist.Cyc$Analysis < 5187.8, "Identifier 1"] <- "all$TV04" #batch 7
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5233 & flatlist.Cyc$Analysis < 5241.8, "Identifier 1"] <- "all$CU TS" #batch 8
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5242 & flatlist.Cyc$Analysis < 5250.8, "Identifier 1"] <- "all$dBBEG" #batch 9
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5251 & flatlist.Cyc$Analysis < 5259.8, "Identifier 1"] <- "all$dBBHG" #batch 10
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5287 & flatlist.Cyc$Analysis < 5295.8, "Identifier 1"] <- "all$CU TS" #batch 11
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5296 & flatlist.Cyc$Analysis < 5304.8, "Identifier 1"] <- "all$eYSHG" #batch 12
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5341 & flatlist.Cyc$Analysis < 5349.8, "Identifier 1"] <- "all$TV04" #batch 13
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5350 & flatlist.Cyc$Analysis < 5358.8, "Identifier 1"] <- "all$eYSHG" #batch 14
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5359 & flatlist.Cyc$Analysis < 5367.8, "Identifier 1"] <- "all$eYSEG" #batch 15
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5386 & flatlist.Cyc$Analysis < 5394.8, "Identifier 1"] <- "all$NBS19" #batch 16
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5406 & flatlist.Cyc$Analysis < 5412.8, "Identifier 1"] <- "all$eYSEG" #batch 17. not enough cycles
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5441 & flatlist.Cyc$Analysis < 5449.8, "Identifier 1"] <- "all$dBBEG" #batch 18
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5450 & flatlist.Cyc$Analysis < 5456.8, "Identifier 1"] <- "all$Carrara.CIT" #batch 19
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5513 & flatlist.Cyc$Analysis < 5521.8, "Identifier 1"] <- "all$dBBHG" #batch 20
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5558 & flatlist.Cyc$Analysis < 5566.8, "Identifier 1"] <- "all$TV04" #batch 21
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5567 & flatlist.Cyc$Analysis < 5575.8, "Identifier 1"] <- "all$NIST 88B" #batch 22
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5577 & flatlist.Cyc$Analysis < 5585.8, "Identifier 1"] <- "all$eYSEG" #batch 23
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5595 & flatlist.Cyc$Analysis < 5603.8, "Identifier 1"] <- "ACF$AF-NCF-TS2-16-10" #batch 24
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5604 & flatlist.Cyc$Analysis < 5612.8, "Identifier 1"] <- "ACF$AF-NCF-TS2-16-12" #batch 25
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5613 & flatlist.Cyc$Analysis < 5621.8, "Identifier 1"] <- "all$TV04" #batch 26
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5622 & flatlist.Cyc$Analysis < 5630.8, "Identifier 1"] <- "ACF$AF-NCF-TS2-16-14" #batch 27
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5632 & flatlist.Cyc$Analysis < 5640.8, "Identifier 1"] <- "all$dBBHG" #batch 28
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5641 & flatlist.Cyc$Analysis < 5649.8, "Identifier 1"] <- "ACF$AF-NCF-TS2-16-25" #batch 29
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5650 & flatlist.Cyc$Analysis < 5658.8, "Identifier 1"] <- "all$NBS18" #batch 30
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5695 & flatlist.Cyc$Analysis < 5703.8, "Identifier 1"] <- "all$eYSHG" #batch 31
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5715 & flatlist.Cyc$Analysis < 5723.8, "Identifier 1"] <- "all$Carrara.CIT" #batch 32
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5724 & flatlist.Cyc$Analysis < 5732.8, "Identifier 1"] <- "ACF$AF-NCF-TS2-16-14" #batch 33
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5733 & flatlist.Cyc$Analysis < 5741.8, "Identifier 1"] <- "ACF$AF-NCF-TS2-16-25" #batch 34
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5742 & flatlist.Cyc$Analysis < 5750.8, "Identifier 1"] <- "all$dBBEG" #batch 35
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5751 & flatlist.Cyc$Analysis < 5759.8, "Identifier 1"] <- "all$CU TS" #batch 36
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5760 & flatlist.Cyc$Analysis < 5768.8, "Identifier 1"] <- "ACF$AF-NCF-TS2-16-26" #batch 37
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5769 & flatlist.Cyc$Analysis < 5777.8, "Identifier 1"] <- "ACF$AF-NCF-TS3-16-01" #batch 38
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5778 & flatlist.Cyc$Analysis < 5786.8, "Identifier 1"] <- "all$NBS18" #batch 39
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5787 & flatlist.Cyc$Analysis < 5795.8, "Identifier 1"] <- "ACF$AF-NCF-TS3-16-17" #batch 40
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5796 & flatlist.Cyc$Analysis < 5804.8, "Identifier 1"] <- "ACF$AF-NCF-TS3-16-15" #batch 41
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5805 & flatlist.Cyc$Analysis < 5813.8, "Identifier 1"] <- "all$TV04" #batch 42
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5814 & flatlist.Cyc$Analysis < 5822.8, "Identifier 1"] <- "all$dBBHG" #batch 43
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5823 & flatlist.Cyc$Analysis < 5831.8, "Identifier 1"] <- "all$Carrara.CIT" #batch 44
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5832 & flatlist.Cyc$Analysis < 5840.8, "Identifier 1"] <- "ACF$AF-NCF-TS2-16-26" #batch 45
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5841 & flatlist.Cyc$Analysis < 5849.8, "Identifier 1"] <- "ACF$AF-NCF-TS3-16-01" #batch 46
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5850 & flatlist.Cyc$Analysis < 5858.8, "Identifier 1"] <- "all$CU TS" #batch 47
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5859 & flatlist.Cyc$Analysis < 5867.8, "Identifier 1"] <- "ACF$AF-NCF-TS3-16-17" #batch 48
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5868 & flatlist.Cyc$Analysis < 5876.8, "Identifier 1"] <- "ACF$AF-NCF-TS2-16-10" #batch 49
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5877 & flatlist.Cyc$Analysis < 5885.8, "Identifier 1"] <- "all$CU YULE" #batch 50
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5886 & flatlist.Cyc$Analysis < 5887.8, "Identifier 1"] <- "all$Sarah CO2 tank" #batch 51
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5888 & flatlist.Cyc$Analysis < 5896.8, "Identifier 1"] <- "all$eYSEG" #batch 52
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5897 & flatlist.Cyc$Analysis < 5905.8, "Identifier 1"] <- "ACF$AF-NCF-TS2-16-12" #batch 53
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5906 & flatlist.Cyc$Analysis < 5914.8, "Identifier 1"] <- "ACF$AF-NCF-TS2-16-14" #batch 54
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5915 & flatlist.Cyc$Analysis < 5923.8, "Identifier 1"] <- "ACF$AF-NCF-TS2-16-25" #batch 55
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5924 & flatlist.Cyc$Analysis < 5932.8, "Identifier 1"] <- "all$NBS18" #batch 56
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5951 & flatlist.Cyc$Analysis < 5959.8, "Identifier 1"] <- "all$dBBEG" #batch 57
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5960 & flatlist.Cyc$Analysis < 5968.8, "Identifier 1"] <- "all$eYSEG" #batch 58
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5969 & flatlist.Cyc$Analysis < 5977.8, "Identifier 1"] <- "all$eYSHG" #batch 59
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 5987 & flatlist.Cyc$Analysis < 5994.8, "Identifier 1"] <- "all$TV04" #batch 60
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 6086 & flatlist.Cyc$Analysis < 6094.8, "Identifier 1"] <- "all$dBBHG" #batch 61
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 6104 & flatlist.Cyc$Analysis < 6112.8, "Identifier 1"] <- "all$Carrara.CIT" #batch 62
 # flatlist.Cyc[  flatlist.Cyc$Analysis > 6149 & flatlist.Cyc$Analysis < 6157.8, "Identifier 1"] <- "all$Carrara.CIT" #batch 63
 # 
 # flatlist.Cyc <- flatlist.Cyc %>% 
 #    change.donotuse.and.runinfo(5886.1, 5887.8,TRUE,"not enough cycles") %>%  #Sarah CO2 tank
 #    change.donotuse.and.runinfo(5613.1, 5621.8, TRUE, "completely offset from rest of TV04") #TV04 

```

### 3524 to 4538 - ACF - AF4

User <- ACF

session <- AF4

session_date_start <- 20170421

session_date_end <- 20170507

session_analysis_start <- 3524

session_analysis_end <- 4538

```{r Data correction info - 3524 to 4538 - ACF - AF4}
# 
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 3524 & flatlist.Cyc$Analysis < 3532.8, "Identifier 1"] <- "all$TV04" #batch 1
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 3533 & flatlist.Cyc$Analysis < 3541.8, "Identifier 1"] <- "all$NBS18" #batch 2
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 3542 & flatlist.Cyc$Analysis < 3550.8, "Identifier 1"] <- "all$Carrara.CIT" #batch 3
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 3551 & flatlist.Cyc$Analysis < 3559.8, "Identifier 1"] <- "all$CIT HIS" #batch 4
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 3560 & flatlist.Cyc$Analysis < 3568.8, "Identifier 1"] <- "all$CU YULE" #batch 5
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 3569 & flatlist.Cyc$Analysis < 3577.8, "Identifier 1"] <- "all$dBBEG" #batch 6
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 3578 & flatlist.Cyc$Analysis < 3586.8, "Identifier 1"] <- "all$Carrara.CIT" #batch 7
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 3587 & flatlist.Cyc$Analysis < 3595.8, "Identifier 1"] <- "all$eYSEG" #batch 8
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 3596 & flatlist.Cyc$Analysis < 3604.8, "Identifier 1"] <- "all$dBBHG" #batch 9
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 3605 & flatlist.Cyc$Analysis < 3613.8, "Identifier 1"] <- "all$NBS18" #batch 10
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 3616 & flatlist.Cyc$Analysis < 3624.8, "Identifier 1"] <- "all$eBBHG" #batch 11
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 3625 & flatlist.Cyc$Analysis < 3633.8, "Identifier 1"] <- "ACF$AF-NCF-TS2-16-03" #batch 14
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 3634 & flatlist.Cyc$Analysis < 3642.8, "Identifier 1"] <- "ACF$AF-NCF-TS2-16-12" #batch 15
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 3643 & flatlist.Cyc$Analysis < 3653.8, "Identifier 1"] <- "all$eYSEG" #batch 16
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 3654 & flatlist.Cyc$Analysis < 3673.8, "Identifier 1"] <- "all$TV04" #batch 17. too many cycles!
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 3674 & flatlist.Cyc$Analysis < 3682.8, "Identifier 1"] <- "all$dBBHG" #batch 18
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 3737 & flatlist.Cyc$Analysis < 3747.8, "Identifier 1"] <- "all$Carrara.CIT" #batch 19
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 3748 & flatlist.Cyc$Analysis < 3748.8, "Identifier 1"] <- "all$eYSEG" #batch 20
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 3749 & flatlist.Cyc$Analysis < 3749.8, "Identifier 1"] <- "all$Carrara.CIT" #batch 21
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 3750 & flatlist.Cyc$Analysis < 3759.8, "Identifier 1"] <- "all$eYSEG" #batch 22
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 3790 & flatlist.Cyc$Analysis < 3798.8, "Identifier 1"] <- "all$dBBEG" #batch 23
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 3866 & flatlist.Cyc$Analysis < 3874.8, "Identifier 1"] <- "all$NBS19" #batch 24
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 3875 & flatlist.Cyc$Analysis < 3883.8, "Identifier 1"] <- "all$eYSHG" #batch 25
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 3884 & flatlist.Cyc$Analysis < 3893.8, "Identifier 1"] <- "all$Carrara.CIT" #batch 26
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 3939 & flatlist.Cyc$Analysis < 3947.8, "Identifier 1"] <- "all$TV04" #batch 27
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 3958 & flatlist.Cyc$Analysis < 3966.8, "Identifier 1"] <- "all$dBBEG" #batch 28
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4021 & flatlist.Cyc$Analysis < 4029.8, "Identifier 1"] <- "all$eYSHG" #batch 29
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4039 & flatlist.Cyc$Analysis < 4047.8, "Identifier 1"] <- "all$NBS19" #batch 30
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4048 & flatlist.Cyc$Analysis < 4056.8, "Identifier 1"] <- "all$TV04" #batch 31
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4057 & flatlist.Cyc$Analysis < 4065.8, "Identifier 1"] <- "all$NBS18" #batch 32
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4066 & flatlist.Cyc$Analysis < 4074.8, "Identifier 1"] <- "ACF$AF-NCF-TS2-16-14" #batch 33
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4076 & flatlist.Cyc$Analysis < 4084.8, "Identifier 1"] <- "all$eYSHG" #batch 34
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4085 & flatlist.Cyc$Analysis < 4093.8, "Identifier 1"] <- "all$dBBEG" #batch 35
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4094 & flatlist.Cyc$Analysis < 4102.8, "Identifier 1"] <- "ACF$AF-NCF-TS2-16-15" #batch 36
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4103 & flatlist.Cyc$Analysis < 4111.8, "Identifier 1"] <- "all$Carrara.CIT" #batch 37
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4112 & flatlist.Cyc$Analysis < 4120.8, "Identifier 1"] <- "ACF$AF-NCF-TS2-16-17" #batch 38
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4121 & flatlist.Cyc$Analysis < 4129.8, "Identifier 1"] <- "ACF$AF-NCF-TS2-16-21" #batch 39
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4130 & flatlist.Cyc$Analysis < 4138.8, "Identifier 1"] <- "all$NBS19" #batch 40
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4139 & flatlist.Cyc$Analysis < 4147.8, "Identifier 1"] <- "all$eYSEG" #batch 41
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4148 & flatlist.Cyc$Analysis < 4156.8, "Identifier 1"] <- "ACF$AF-NCF-TS2-16-22" #batch 42
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4157 & flatlist.Cyc$Analysis < 4165.8, "Identifier 1"] <- "ACF$AF-NCF-TS2-16-25" #batch 43
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4166 & flatlist.Cyc$Analysis < 4174.8, "Identifier 1"] <- "all$TV04" #batch 44
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4175 & flatlist.Cyc$Analysis < 4183.8, "Identifier 1"] <- "ACF$AF-NCF-TS2-16-26" #batch 45
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4184 & flatlist.Cyc$Analysis < 4192.8, "Identifier 1"] <- "ACF$AF-NCF-TS3-16-36" #batch 46
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4193 & flatlist.Cyc$Analysis < 4201.8, "Identifier 1"] <- "all$CU TS" #batch 47
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4203 & flatlist.Cyc$Analysis < 4211.8, "Identifier 1"] <- "all$dBBHG" #batch 48
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4212 & flatlist.Cyc$Analysis < 4220.8, "Identifier 1"] <- "ACF$AF-NCF-TS2-16-35" #batch 49
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4221 & flatlist.Cyc$Analysis < 4229.8, "Identifier 1"] <- "all$TV04" #batch 50
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4230 & flatlist.Cyc$Analysis < 4238.8, "Identifier 1"] <- "ACF$AF-NCF-TS3-16-01" #batch 51
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4239 & flatlist.Cyc$Analysis < 4247.8, "Identifier 1"] <- "ACF$AF-NCF-TS3-16-02" #batch 52
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4248 & flatlist.Cyc$Analysis < 4256.8, "Identifier 1"] <- "all$NBS19" #batch 53
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4257 & flatlist.Cyc$Analysis < 4265.8, "Identifier 1"] <- "ACF$AF-NCF-TS3-16-03" #batch 54
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4266 & flatlist.Cyc$Analysis < 4274.8, "Identifier 1"] <- "ACF$AF-NCF-TS3-16-10" #batch 55
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4275 & flatlist.Cyc$Analysis < 4283.8, "Identifier 1"] <- "all$eYSEG" #batch 56
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4284 & flatlist.Cyc$Analysis < 4292.8, "Identifier 1"] <- "all$Carrara.CIT" #batch 57
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4293 & flatlist.Cyc$Analysis < 4301.8, "Identifier 1"] <- "ACF$AF-NCF-TS3-16-12" #batch 58
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4302 & flatlist.Cyc$Analysis < 4310.8, "Identifier 1"] <- "ACF$AF-NCF-TS3-16-15" #batch 59
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4311 & flatlist.Cyc$Analysis < 4319.8, "Identifier 1"] <- "all$NBS18" #batch 60
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4320 & flatlist.Cyc$Analysis < 4328.8, "Identifier 1"] <- "ACF$AF-NCF-TS2-16-03" #batch 61
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4329 & flatlist.Cyc$Analysis < 4337.8, "Identifier 1"] <- "ACF$AF-NCF-TS3-16-17" #batch 62
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4338 & flatlist.Cyc$Analysis < 4346.8, "Identifier 1"] <- "ACF$AF-NCF-TS3-16-19" #batch 63
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4337 & flatlist.Cyc$Analysis < 4356.8, "Identifier 1"] <- "all$Carrara.CIT" #batch 64
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4357 & flatlist.Cyc$Analysis < 4365.8, "Identifier 1"] <- "all$dBBEG" #batch 65
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4366 & flatlist.Cyc$Analysis < 4374.8, "Identifier 1"] <- "all$Carrara.CIT" #batch 66
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4375 & flatlist.Cyc$Analysis < 4384.8, "Identifier 1"] <- "all$TV04" #batch 67
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4385 & flatlist.Cyc$Analysis < 4393.8, "Identifier 1"] <- "all$CU TS" #batch 68
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4394 & flatlist.Cyc$Analysis < 4402.8, "Identifier 1"] <- "all$NBS19" #batch 69
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4403 & flatlist.Cyc$Analysis < 4411.8, "Identifier 1"] <- "ACF$AF-NCF-TS3-16-19" #batch 70
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4412 & flatlist.Cyc$Analysis < 4420.8, "Identifier 1"] <- "ACF$AF-NCF-TS3-16-15" #batch 71
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4421 & flatlist.Cyc$Analysis < 4429.8, "Identifier 1"] <- "all$dBBHG" #batch 72
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4430 & flatlist.Cyc$Analysis < 4438.8, "Identifier 1"] <- "all$CU TS" #batch 73
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4439 & flatlist.Cyc$Analysis < 4447.8, "Identifier 1"] <- "ACF$AF-NCF-TS3-16-12" #batch 74
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4448 & flatlist.Cyc$Analysis < 4456.8, "Identifier 1"] <- "ACF$AF-NCF-TS3-16-10" #batch 75
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4457 & flatlist.Cyc$Analysis < 4465.8, "Identifier 1"] <- "all$NBS18" #batch 76
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4466 & flatlist.Cyc$Analysis < 4474.8, "Identifier 1"] <- "ACF$AF-NCF-TS3-16-02" #batch 77
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4475 & flatlist.Cyc$Analysis < 4475.8, "Identifier 1"] <- "all$NBS19" #batch 78
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4476 & flatlist.Cyc$Analysis < 4484.8, "Identifier 1"] <- "ACF$AF-NCF-TS2-16-36" #batch 79
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4485 & flatlist.Cyc$Analysis < 4493.8, "Identifier 1"] <- "all$eYSEG" #batch 80
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4494 & flatlist.Cyc$Analysis < 4502.8, "Identifier 1"] <- "all$NBS19" #batch 81
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4503 & flatlist.Cyc$Analysis < 4511.8, "Identifier 1"] <- "ACF$AF-NCF-TS2-16-17" #batch 82
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4512 & flatlist.Cyc$Analysis < 4520.8, "Identifier 1"] <- "ACF$AF-NCF-TS2-16-02" #batch 83
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4521 & flatlist.Cyc$Analysis < 4529.8, "Identifier 1"] <- "all$Carrara.CIT" #batch 84
#  flatlist.Cyc[  flatlist.Cyc$Analysis > 4530 & flatlist.Cyc$Analysis < 4538.8, "Identifier 1"] <- "all$CU YULE" #batch 85
#  
# flatlist.Cyc <- flatlist.Cyc %>% 
#     change.donotuse.and.runinfo(4214, 4220.8,TRUE,"not enough cycles") %>%  #AF-NCF-TS2-16-35 batch45
#     change.donotuse.and.runinfo(4386, 4393.8, TRUE, "not enough cycles") %>% #CU TS batch62
#     change.donotuse.and.runinfo(4067, 4074.8, TRUE, "not enough gas") %>% #AF-NCF-TS2-16-14 batch 28
#     change.donotuse.and.runinfo(4343, 4346.8, TRUE, "not enough gas") %>% #Carrara.CIT batch58
#     change.donotuse.and.runinfo(3750, 3759.8, TRUE, "offset from the rest of population") %>% #eYS batch17
#     change.donotuse.and.runinfo(4338, 4346.8, TRUE, "offset from the rest of population") %>% #Carrara.CIT batch58
#     change.donotuse.and.runinfo(3738, 3747.8, TRUE, "offset from the rest of population") #Carrara.CIT batch 16
```

### 2644 to 3333 - ACF - AF3

User <- ACF

session <- AF3

session_date_start <- 20170225

session_date_end <- 20170317

session_analysis_start <- 2644

session_analysis_end <- 3333

```{r Data correction info - 2644 to 3333 - ACF - AF3}

#note from ACF 20200928 - searched and cannot find data correction/processing content for AF3, except for this note: "Ran throughout 02/25/2017 to 03/17/2017. Took a few standards from May to complete the reference frame (have enought TV04 to correct using Katie's code). I'm dubious about trusting replicates from this session b/c of the weak reference frame. 

```

##### note that AF1-AF2 don't really exist bc they were session where I was learning data production and I don't have data processing record of those times, but I started my session numbering system at AF3 (idk, early grad school decisions...). Also I didn't start to consistently use AF# format until AF6, so there are mismatched session labels. 